Placeholder

### 2021-02-13 Paper_Histograms.Rmd
Added black axis text to retro, gender, age, ethnicity, employ and combined retro graphs

retro_gender_plot <- dat.retro %>% 
  ggplot(aes(x = Gender_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

retro_age_plot <- dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Age (years)",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank())

@@

retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n), 
            position = position_dodge(width=0.9), 
            vjust=-0.25)

#Graph 2
retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
theme(axis.text.x = element_text(angle = 70, 
                                 vjust = 0.5,
                                 size = 8)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))

@@

@@

retro_employ_plot <- dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000))

@@

#Graph 2
arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  #theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))

@@

arranged_retro_age_plot <- dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Age (years)",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5))

@@

arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants",
       caption = "Non-binary/Self-defined
         GLAD/EDGI (243); NBR (39); RAMP (92)") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())

arranged_employ_plot <- dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 3),
                   expand = expansion(mult = c(0.2, 0.3)))

>>>>

retro_gender_plot <- dat.retro %>% 
  ggplot(aes(x = Gender_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

retro_age_plot <- dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Age (years)",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n), 
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

#Graph 2
retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
theme(axis.text.x = element_text(angle = 45, 
                                 vjust = 0.5,
                                 size = 8)) +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2)))  +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

```{r Ethnicity retro pie chart by sample}

@@

retro_employ_plot <- dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "bottom") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

arranged_retro_ethnicity_white <- dat.retro_ethnicity_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))# +
#  geom_text(aes(label = n),
#            size = 3,
#            position = position_dodge(width=0.9), 
#            vjust=-0.25)

#Graph 2
arranged_retro_ethnicity_non_white <- dat.retro_ethnicity_non_white %>% 
  ggplot(aes(x = Ethnicity_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "",
       x = "Ethnic origin",
       y = "N participants") +
  theme(legend.position = "bottom") +
  theme(legend.title = element_blank()) +
  #theme(legend.title = element_blank()) +
  geom_text(aes(label = n),
            size = 3,
            position = position_dodge(width=0.9), 
            vjust=-0.25) +
     scale_y_continuous(expand = expansion(mult = c(0.1, 0.2))) +
  scale_x_discrete(guide = guide_axis(n.dodge = 2)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

arranged_retro_age_plot <- dat.retro %>% 
  ggplot(aes(x = age_category_collapsed, fill = Sample_plot)) +
  geom_bar(position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Age (years)",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  theme(axis.text.x = element_text(angle = 70, vjust = 0.5)) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

@@

arranged_collapsed_gender_plot <- dat.retro_gender_male_female %>% 
  ggplot(aes(x = Gender_collapsed, y = n, fill = Sample_plot)) +
  geom_bar(position = "dodge", stat = "identity") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Participant Gender",
       y = "N participants",
       caption = "Non-binary/Self-defined
         GLAD/EDGI (243); NBR (39); RAMP (92)") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank())  +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))

arranged_employ_plot <- dat.retro_employment_plot %>% 
  ggplot(aes(x = employment_prior_covid, y = n, fill = Sample_plot)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_fill_manual(values = COPINGpalette3) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(x = "Employment status",
       y = "N participants") +
  theme(legend.position = "none") + 
  theme(legend.title = element_blank()) +
  scale_y_continuous(breaks = seq(0, 6000, by = 1000)) +
  scale_x_discrete(guide = guide_axis(n.dodge = 3),
                   expand = expansion(mult = c(0.2, 0.3))) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))
